Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-02-23 Paper/paper.tex

% Macros for text notes and comments
\newcommand{\Note}[1]{\textcolor{blue}{\textbf{[#1]}}}
\newcommand{\lambdans}{\Lambda_\mathrm{NS}}
\newcommand{\chibh}{\chi_\mathrm{BH}}
\newcommand{\chins}{\chi_\mathrm{NS}}
\newcommand{\mbh}{m_\mathrm{BH}}
\newcommand{\mns}{m_\mathrm{NS}}
\newcommand{\mchirp}{\mathcal{M}_c}

@@

\subsection{MCMC methods}
Describe the emcee-based PE code

>>>>

% Macros for text notes and comments
\newcommand{\Note}[1]{\textcolor{blue}{\textbf{[#1]}}}
\newcommand{\lambdans}{\Lambda_\mathrm{NS}}
\newcommand{\chibh}{\chi_\mathrm{BH}}
\newcommand{\chins}{\chi_\mathrm{NS}}
\newcommand{\mbh}{m_\mathrm{BH}}
\newcommand{\mns}{m_\mathrm{NS}}
\newcommand{\mchirp}{\mathcal{M}_c}
\newcommand{\LL}{\mathcal{L}}

@@

\subsection{MCMC methods}
% % Describe the emcee-based PE code

The monte carlo algorithm samples the parameter space in proportion with 
the likelihood $\LL(\vec{\theta}) = p(d|\vec{\theta})$, with a 
uniform prior in parameters $p(\vec{\theta}) = \Theta(\vec{\theta}-\vec{\theta}_L) + \Theta(\vec{\theta}_H-\vec{\theta})$
\begin{equation}
 p(\vec{\theta}|d) = p(d|\vec{\theta}) p(\vec{\theta})
\end{equation}
